Which Scenario Should We Design For? Insights from House Elevation on the Multiple PDF Problem

### 2021-10-13 papers/operationalizing-bayesian-checking.tex
Updates from Overleaf

% authors
\usepackage{authblk}
\title{Which Scenario Should We Design For? Insights from House Elevation on the Multiple PDF Problem}
\author[1]{James Doss-Gollin}
\author[2,3,4]{Klaus Keller}
\affil[1]{Department of Civil and Environmental Engineering, Rice University}
\affil[2]{Department of Geosciences, the Pennsylvania State University}
\affil[3]{Earth and Environmental Systems Institute, the Pennsylvania State University}
\affil[4]{Dartmouth?}
\renewcommand*{\Affilfont}{\normalsize\normalfont}

@@

% use biblatex
\usepackage{csquotes}
\usepackage[
  backend=biber,
  doi=true,
  url=false,
  isbn=false,
  style=authoryear-comp,
  natbib=true,
  backref=false,
  maxbibnames=10,
  maxcitenames=2,
  uniquename=false,
  uniquelist=false,
  sorting=nyt,
]{biblatex}
\renewbibmacro{in:}{}
\AtEveryBibitem{\clearfield{month}\clearfield{day}\clearfield{pages}\clearlist{language}}
\addbibresource{../_bibliography/library.bib}

@@

\subsection*{Submission Plan}
We should revisit this!
\begin{enumerate}
    \item Climatic Change
    \item IOP Environmental Research: Infrastructure and Sustainability (new journal)
    \item Earth's Future
    \item Risk analysis
\end{enumerate}
\subsection*{Internal peer review}
\begin{enumerate}
    \item TBD
\end{enumerate}

@@

\paragraph{Why this problem is important}
Since infrastructure built today is likely to persist for several decades, infrastructure designs must take into account the stresses that a project is likely to face far into the future.
On the one hand, overly optimistic assumptions of future risk can lead to unacceptably high risk of failure in the future if additional investments are not made.
For example, a failure to prepare Texas's interconnected natural gas, electricity, and water systems for temperatures that had been observed in the past 30 years caused cascading failures with disparate impacts \citep{doss-gollin_codes_txtreme:2021}.
On the other, unless opportunity costs are negligible, designing for a too-pessimistic scenario can contribute to maladptation by limiting resource availability in the future.
For example, (\texttt{megaproject example})\ldots.

@@

                        \item Stormwater management \citep{sharma_stormwater:2021,lopez-cantu:2018}

>>>>

% authors
\usepackage{authblk}
\title{Which Scenario Should We Design For? Insights from House Elevation on the Multiple PDF Problem}
\author[1]{James Doss-Gollin}
\author[2,3,4]{Klaus Keller}
\affil[1]{Department of Civil and Environmental Engineering, Rice University}
\affil[2]{Department of Geosciences, the Pennsylvania State University}
\affil[3]{Earth and Environmental Systems Institute, the Pennsylvania State University}
\affil[4]{Thayer School of Engineering, Dartmouth College}
\renewcommand*{\Affilfont}{\normalsize\normalfont}

@@

% use biblatex
\usepackage{csquotes}
\usepackage[
  backend=biber,
  doi=true,
  url=false,
  isbn=false,
  style=authoryear-comp,
  natbib=true,
  backref=false,
  maxbibnames=10,
  maxcitenames=2,
  uniquename=false,
  uniquelist=false,
  sorting=nyt,
]{biblatex}
\renewbibmacro{in:}{}
\AtEveryBibitem{\clearfield{month}\clearfield{day}\clearfield{pages}\clearlist{language}}
%\addbibresource{../_bibliography/library.bib}
\addbibresource{library.bib}

@@

\subsection*{Submission Plan}
We should revisit this!
\begin{enumerate}
    \item Earth's Future
    \item Climatic Change
    \item IOP Environmental Research: Infrastructure and Sustainability (new journal)
    \item Risk analysis
\end{enumerate}
\subsection*{Internal peer review}
\begin{enumerate}
    \item TBD
\end{enumerate}

@@

\paragraph{Why this problem is important}
Since infrastructure built today is likely to persist for several decades, infrastructure designs must take into account the stresses that a project is likely to face far into the future.
On the one hand, overly optimistic assumptions of future risk can lead to unacceptably high risk of failure in the future if additional investments are not made.
For example, a failure to prepare Texas's interconnected natural gas, electricity, and water systems for temperatures that had been observed in the past 30 years caused cascading failures with disparate impacts \citep{doss-gollin_txtreme:2021}.
On the other, unless opportunity costs are negligible, designing for a too-pessimistic scenario can contribute to maladptation by limiting resource availability in the future.
For example, (\texttt{megaproject example})\ldots.

@@

                        \item Stormwater management \citep{sharma_rcp:2021,lopez-cantu:2018}
